Discussion Draft

### 2020-03-17 doc/Discussion.rmd
more edits

Petkov paper -- states that the sexual dimorphism for interference strength is due to the chromatin structure (meiotic chromosome organization) with the increased interference strength in males being due to longer chromatin loop lengths.

  it boils down to, the relationship with axis length and DNA loop size --

  --females have shorter loops - longer axis and weaker interference

  Chromatin structure -- the size / length of meiotic chromosomes

  same pattern in humans (Gruhn et al 2013)

  (exceptions, birds (fish?) plants?) -- examining this is hard due to chromosome size effecs

  - This also assumes that the DNA loop sizes have uniform size along and between chromosomes

@@

## Greater Within mouse variance in female

@@

We did not observe

- Because these are inbred strains raised in common / standard lab environment, (an single levels)

@@

-age differences

new paper has revealed within nucleus variation for (CO number -- potentially via the chromatin remodeling) (Veller Kleckner)

 Gruhn et al 2013 (the favorite figures)

 Gruhn et al 2016 -- not due to the developmental stage of the oocytes (ovulation) (the production line)

 mouse and humans show greater between cell variance -- this metric isn't really focused on (not many studies that examine inidivial level and both sexes)

3. Within mouse variance differences
In our results we observe more between cell variance in females (across all strains). This pattern has been observed in humans (Lynn et al). (But results of reporting observations of single meiosis in both sexes).

@@

(Gruhn et al), Kong et al?

cattle,

- age effects?

- Hassold hunt

_Relaxed selection_ leads to

>>>>

< Petkov paper -- states that the sexual dimorphism for interference strength is due to the chromatin structure (meiotic chromosome organization) with the increased interference strength in males being due to longer chromatin loop lengths.>

<same pattern in humans (Gruhn et al 2013)
  (exceptions, birds (fish?) plants?) -- examining this is hard due to chromosome size effecs
  - This also assumes that the DNA loop sizes have uniform size along and between chromosomes>

@@

## Greater within mouse variance in female

```{r within.mouse.var, include=FALSE}

#our results, female more (greater than tech error) male no significant difference

#-replicate some previous results
#(Gruhn et al), Kong et al?, cattle,

#between cell variance (Veller Kleckner), mechnism
#evolution / popgen model from (veller)

#sources of within mouse variance; age effects,  Hassold hunt

#models that predict more within animal variance

##connection on evolution of transcriptional noise

@@

@@

 mouse and humans show greater between cell variance -- [@]

 this metric isn't really focused on (not many studies that examine inidivial level and both sexes)

3. Within mouse variance differences
In our results we observe more between cell variance in females (across all strains). This pattern has been observed in humans (Lynn et al).[@lynn2002]
(But results of reporting observations of single meiosis in both sexes).

@@
